---
title: "Korean Drama Analysis"
author: "Nithisha, Vinnie, Miao, Brandon"
date: "`r Sys.Date()`" #dynamic date
output: 
  html_document:
    toc: true # table of content
    toc_float: true # float 
---

## Introduction

What factors, such as release year, genre, tags, screenwriter, and duration, influence the success of a K-drama in terms of ratings?

<!-- Preparing the Data -->
```{r message=FALSE, warning=FALSE, echo = FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(viridis)  

kdrama <- read.csv("kdrama.csv")
```

## Number of K-Dramas Released Over the Years

```{r pressure, echo=FALSE}

# Number of Kdrama based on released year
kdrama %>%
  ggplot(aes(x = factor(Year.of.release), fill = Year.of.release)) + 
  geom_bar() +
  scale_fill_viridis_c() +  # Adds a visually appealing color gradient
  labs(
    x = "Year",
    y = "Number of K-Dramas"
  ) + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels
  ) 
```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## K-Drama Ratings by Network

```{r rating by orginal Network, echo=FALSE}
# Ratings by Original Network
ggplot(kdrama, aes(x = reorder(Original.Network, Rating, median, na.rm = TRUE), 
                    y = Rating, fill = Original.Network)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +  # Hide outliers for clarity
  labs(
    x = "Original Network", 
    y = "Rating"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none", 
    axis.text.x = element_text(angle = 60, hjust = 1)
  ) +
  scale_fill_viridis_d() 
```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## Influence of Episode Duration on K-Drama Ratings

```{r kdrama_by_year, echo=FALSE}
# Function to convert duration strings into total minutes
convert_to_minutes <- function(time) {
  hours <- as.numeric(str_extract(time, "\\d+(?= hr)"))  # Extract hours
  minutes <- as.numeric(str_extract(time, "\\d+(?= min)"))  # Extract minutes
  
  hours[is.na(hours)] <- 0  # Replace NA when no hours present
  minutes[is.na(minutes)] <- 0  # Replace NA when no minutes present
  
  return(hours * 60 + minutes)  # Convert to total minutes
}

# Convert the Duration column
kdrama <- kdrama %>%
  mutate(Duration_Minutes = sapply(Duration, convert_to_minutes))

# Define 30-minute interval bins
breaks_seq <- seq(0, max(kdrama$Duration_Minutes, na.rm = TRUE) + 30, by = 30) 
labels_seq <- paste0(head(breaks_seq, -1), "-", tail(breaks_seq, -1) - 1, " min")

# Assign bins
kdrama <- kdrama %>%
  mutate(Time_Group = cut(Duration_Minutes, 
                          breaks = breaks_seq, 
                          labels = labels_seq, 
                          right = FALSE)) 

# Compute mean rating per duration group
duration_summary <- kdrama %>%
  group_by(Time_Group) %>%
  summarise(Average_Rating = mean(Rating, na.rm = TRUE))

# Plot: Influence of Duration on K-Drama Ratings
ggplot(duration_summary, aes(x = Time_Group, y = Average_Rating, fill = Time_Group)) +
  geom_col() +  # Use geom_col() instead of geom_bar(stat = "identity")
  scale_fill_viridis_d() +  # Improved color scheme
  labs(
    x = "Duration Interval (minutes)",
    y = "Average Rating"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),  # Rotate x-axis labels
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14)  # Center and bold title
  )
```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## Most Popular Genres

```{r Most popular genres, echo=FALSE}
genre_counts <- kdrama %>%
  separate_rows(Genre, sep = ", ") %>%
  mutate(Genre = str_trim(Genre)) %>%  # Trim extra spaces
  mutate(Genre = str_to_title(Genre)) %>%  # Standardize capitalization
  count(Genre, sort = TRUE) %>%
  distinct(Genre, .keep_all = TRUE) %>%  # Remove duplicates
  slice_max(n, n = 10)  # Select exactly the top 10 genres

ggplot(genre_counts, aes(x = reorder(Genre, n), y = n, color = Genre)) +
  geom_point(size = 3) +  # Using points instead of bars
  geom_segment(aes(xend = Genre, yend = 0), color = "darkblue") +  # Add lines from points to the x-axis
  labs(
    x = "Genre",
    y = "Number of K-Dramas"
  ) +
  theme_minimal() +
  scale_color_viridis_d() +
  theme(legend.position = "none", axis.text.x = element_text( ))

```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## Top 10 Directors with the Highest Average Ratings

```{r Directors and avg rating, echo=FALSE}
top_directors <- kdrama %>%
  group_by(Director) %>%
  summarise(Average_Rating = mean(Rating, na.rm = TRUE), Count = n()) %>%
  filter(Count >= 3) %>%  # Consider directors with at least 3 dramas
  arrange(desc(Average_Rating)) %>%
  head(10)

ggplot(top_directors, aes(x = reorder(Director, Average_Rating), y = Average_Rating, fill = Director)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "Director",
    y = "Average Rating"
  ) +
  theme_minimal() +
  scale_fill_viridis_d() +
  theme(legend.position = "none")
```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## Ratings by Content Rating based on Age Group

```{r Age Group, warning = FALSE, echo=FALSE}
# Filter out the unwanted categories
filtered_kdrama <- kdrama %>%
  filter(!is.na(Content.Rating) & Content.Rating != "G - All Ages")

# Create the violin plot without the removed categories
ggplot(filtered_kdrama, aes(x = Content.Rating, y = Rating, fill = Content.Rating)) +
  geom_violin(trim = FALSE) +
  labs(
    x = "Content Rating",
    y = "Rating"
  ) +
  theme_minimal() +
  scale_fill_viridis_d() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

rating_trend <- filtered_kdrama %>%
  group_by(Year.of.release) %>%
  summarise(Average_Rating = mean(Rating, na.rm = TRUE))
```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## Average Rating of K-Dramas Over the Years

```{r Average Rating, warning = FALSE, echo=FALSE}
ggplot(rating_trend, aes(x = Year.of.release, y = Average_Rating)) + 
  geom_line(color = "red", size = 1) +
  geom_point(color = "darkred", size = 2) +
  labs(
    title = "Average K-Drama Ratings Over the Years",
    x = "Year",
    y = "Average Rating"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14))
```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

## Top 10 Screenwriters with Highest Average Ratings

```{r Screenwriters Rating, warning = FALSE, echo=FALSE}
# Calculate the top screenwriters based on their average rating
top_screenwriters <- kdrama %>%
  group_by(Screenwriter) %>%
  summarise(Average_Rating = mean(Rating, na.rm = TRUE), Count = n()) %>%
  filter(Count >= 3) %>%  # Consider screenwriters with at least 3 dramas
  arrange(desc(Average_Rating)) %>%
  head(10)

# Scatter plot to represent the top screenwriters
ggplot(top_screenwriters, aes(x = reorder(Screenwriter, Average_Rating), y = Average_Rating, size = Count, color = Average_Rating)) +
  geom_point() +
  coord_flip() +
  labs(
    title = "",
    x = "Screenwriter",
    y = "Average Rating"
  ) +
  theme_minimal() +
  scale_color_viridis_c() +
  theme(legend.position = "none")

```

Based on the graph create using our data set, we can observe a **steady increase in the number of Korean dramas produced each year**. For instance, in 2015, only 9 dramas were released, whereas in 2021, the number rose significantly to 39. This trend highlights the growing popularity and demand for Korean dramas over time.

# 2. Conclusions

We suggest that ozone is highly correlated with temperature, but that a different relationship exists for each geographic region

