---
title: "BDATA 200 Reproducibility Exercise"
author: 'Kevin Garcia '
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: '3'
    df_print: paged
    number_sections: true
    theme: united
    code_folding: none
  pdf_document:
    toc: true
    toc_depth: '3'
  word_document:
    toc: true
    toc_depth: '3'
---

# Setup code


## Load Required Packages
```{r load-packages}
library(ggplot2)
library(dplyr)
```

## Load the Data
```{r load-data}
setwd("/Users/nithishasathishkumar/Desktop/Data_Analysis/R/Class_exercise")
titanic <- read.csv("TitanicData.csv")
```

## Data Preprocessing
we convert categorical variables (`survived` and `pclass`) into factors for better readability and visualization.

```{r preprocess-data}
titanic$survived <- factor(titanic$survived, labels = c("Did Not Survive", "Survived"))
titanic$pclass <- factor(titanic$pclass, labels = c("1st Class", "2nd Class", "3rd Class"))
```

# Chart/Graph Code
The following visualization shows the survival rate by passenger class.

```{r plot-survival-rate}
# Plot survival rate by passenger class
ggplot(titanic, aes(x = pclass, fill = survived)) +
  geom_bar(position = "fill") +
  labs(title = "Titanic Survival Rate by Passenger Class", 
       x = "Passenger Class", 
       y = "Proportion", 
       fill = "Survival Status") +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()
```

# Additional Notes on Reproducibility
- make sure the dataset file (`TitanicData.csv`) is in the working directory before running the code

